Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-12-09 ms.tex
working on temperature offsets and correlations.
added results of temperature correlations

>>>>

\clearpage
\subsubsection{Box Temperature}
The box temperature leads the flux variations by 4.9 minutes, likely due to the thermal delay between the box and the LED mounted to the box.

\begin{figure*}
{\gridline{\fig{azlab08_sub320_multiexp_temp_correlation.pdf}{0.48\textwidth}{Sub 320 Multi-exposure test}
\fig{azlab08_sub320_lakeshore_tchange_temp_correlation.pdf}{0.48\textwidth}{Lakeshore Temp Change}}}
\caption{Two separate time series show the same correlation with Box Temperature after removing the 4.9 hour time offset}
\end{figure*}
